---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  out.width = "100%"
)
```

# Coral Metabolomics: Classification of Corals Exposed to Elevated Temperature and Carbon Dioxide

<!-- badges: start -->
[![License: CC BY 4.0](https://img.shields.io/badge/License-CC%20BY%204.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)
<!-- badges: end -->

This repositry contains the data and analysis of research into the effects of ocean acidification and warming on the metabolome of *Acropora aspera*. It is provided as an R package to ensure reproducibility while adopting a common standard project structure; and to explore the merits of doing so. It provides funcions for all steps of the analysis including preprocessing, modelling as well as figure and table generation. 

Please note that this package and its functions have been written explicitly for this project and may have limited use outside of the package.

### Package Structure
* [data](data/): Contains the preprocessed data as R data files.
* [data-raw](data-raw/) : Contains the raw data and a small subset of the raw LCMS data.
* [inst](inst/) : Contains installed files and data.
* [man](man/): Contains the function and dataset documentation files.
* [R](R/): Contains the function scripts used in the analysis.

### Usage
You can install coralclass in R using the devtools package:

```{r pck_install, eval=FALSE}
devtools::install_github("brgordon17/coralclass")
```

### License
Creative Commons Attribution 4.0 International Public License

For more information, please see the [LICENSE](LICENSE.md) file.


