---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# gordon01

CHANGE!!! zenodo DOI badge
[![DOI](https://zenodo.org/badge/6271972.svg)](https://zenodo.org/badge/latestdoi/6271972)

### Authors
* Benjamin R. Gordon
* Check if I should add others? I may not need to if it's a thesis repo.

### Contributors
* Other "authors" may be able to go here instead of into the authors section.

### Overview
This repositry contains the data and analysis of our research into the effects
of ocean acidification and warming on the metabolome of the coral 
*Acopora aspera*. It has been permanantly archived at the DOI indicated by the 
above linked badge.

### R Package
This repositry is organised as an R package to ensure reproducibility of our
analysis. It provides funcions for all steps of the analysis including 
**preprocessing**, **modelling** as well as **figure and table generation**.
Please note that this package and its functions have been written explicitly for
this project and may have limited use outside of the package.

[![Travis-CI Build Status](https://travis-ci.org/<USERNAME>/<REPO>.svg?branch=master)](https://travis-ci.org/<USERNAME>/<REPO>)

### Package Structure
* `data/`: Contains the preprocessed data as R data files.
* `data-raw/`: Contains the raw data and a small subset of our `.mzXML` data
* `inst/`: Contains the `extdata/` folder that holds `.csv` files of the
preprocessed data.
* `man/`: Contains the function and dataset documentation.
* `R/`: Contains the custom functions used in the analysis.

### Pacakage Installation
To install this package within R, ensure you have `devtools::` installed and 
enter the code below at the R prompt:
```{r pck_install, eval=FALSE}
devtools::install_github("brgordon17/gordon01")
```

### Citation
Add citation

### R Session Information
```{r session}
devtools::session_info()
```

