---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  out.width = "100%"
)
```

# Coral Metabolomics: Classification of Corals Exposed to Elevated Temperature and Carbon Dioxide

<!-- badges: start -->
[![License: CC BY 4.0](https://img.shields.io/badge/License-CC%20BY%204.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)
<!-- badges: end -->

This repositry contains the data and analysis of my research into the effects of ocean acidification and warming on the metabolome of *Acopora aspera*. It is provided as an R package to ensure reproducibility while adopting a common standard project structure, and to explore the merits of doing so. It provides funcions for all steps of the analysis including preprocessing, modelling as well as figure and table generation. 

Please note that this package and its functions have been written explicitly for this project and may have limited use outside of the package.

### Package Structure
* [data](data/): Contains the preprocessed data as R data files.
* [data-raw](data-raw/) : Contains the raw data and a small subset of the raw LCMS data
* [inst](inst/) : Contains the `extdata/` folder that holds `.csv` files of the
preprocessed data.
* `man/`: Contains the function and dataset documentation.
* `R/`: Contains the custom functions used in the analysis.

### Pacakage Installation
To install this package within R, ensure you have `devtools::` installed and 
enter the code below at the R prompt:
```{r pck_install, eval=FALSE}
devtools::install_github("brgordon17/gordon01")
```
